A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-04-22 paper/paper.Rnw
add commenting, fix errors, add 'todos'

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks.

@@

\paragraph{VGG16}
Developed by Oxford's Visual Graphics Group, VGG16 is a CNN with 16 ``\functional" (i.e., convolutional and densely connected) layers and 5 ``\structural" max pooling layers\citep{krizhevskyImageNetClassificationDeep2012}. In contrast to other popular networks, like ResNet, VGG has a relatively simple structure that provides easier training and interpretability with very little sacrificed accuracy. The simplicity of this structure provides the ability to peer into the inner workings of the network for diagnostic purposes, providing a distinct advantage over more complicated network structures with slightly higher accuracy ratings.

>>>>

%%% Commenting %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[table]{xcolor}
\newcommand{\mt}[1]{{\color{magenta} #1}}
\newcommand{\svp}[1]{{\color{teal} #1}}
\newcommand{\fix}[1]{{\color{orange} #1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Many convolutional neural networks have been trained on a set of images known as ImageNet; these images are hierarchically labeled, so the same image of a dog may have labels of sky, grass, and trees, and the dog may be labeled as ``mammal'', ``dog'', ``retriever'', and ``golden retriever'' at increasing levels of label complexity\fix{cite imagenet here}. CNNs trained on ImageNet are optimized for general human-like vision, that is, the ability to recognize a large set of different features simultaneously. As a result, the base of networks trained on these sets are often used for transfer learning, because the initial layers are broadly generalizable to a wide variety of more specific image labeling tasks. \fix{add a few VGG16 filters here to demonstrate the generic filters in layers 1-4}

@@

\paragraph{VGG16}
Developed by Oxford's Visual Graphics Group, VGG16 is a CNN with 16 ``functional" (i.e., convolutional and densely connected) layers and 5 ``structural" max pooling layers\citep{krizhevskyImageNetClassificationDeep2012}. In contrast to other popular networks, like ResNet, VGG has a relatively simple structure that provides easier training and interpretability with very little sacrificed accuracy. The simplicity of this structure provides the ability to peer into the inner workings of the network for diagnostic purposes, providing a distinct advantage over more complicated network structures with slightly higher accuracy ratings.
